Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-11 paper/paper.tex
generic related work

Program synthesis is the mechanized construction of software that provably
satisfies a given specification.  Synthesis tools promise to relieve the
programmer from thinking about \emph{how} the problem is to be solved;
instead, the programmer only provides a compact description of \emph{what}
is to be achieved.  Foundational research in this area has been
exceptionally fruitful, beginning with Alonzo Church's work on the
\emph{Circuit Synthesis Problem} in the sixties~\cite{church-synth}.
Since then the program synthesis problem for programs has been attacked by Manna
and Waldinger using theorem provers~\cite{manna-waldinger}, and by
Kraan et al. using proof planning techniques~\cite{proof-planning}.

>>>>

Program synthesis is the mechanized construction of software that provably
satisfies a given specification.  Synthesis tools promise to relieve the
programmer from thinking about \emph{how} the problem is to be solved;
instead, the programmer only provides a compact description of \emph{what}
is to be achieved.  Foundational research in this area has been
exceptionally fruitful, beginning with Alonzo Church's work on the
\emph{Circuit Synthesis Problem} in the sixties~\cite{church-synth}.
Algorithmic approaches to the problem have frequently been connected to
automated theorem proving~\cite{manna-waldinger,proof-planning}.
